%% If you edit this, make sure to update the amended date!

\input{formatting}

\amended{2017-11-14}

\begin{document}
\maketitlepage{Bylaws}

\section{General}

% These are included from an external file so that they remain synchronized
% with the ones in the constitution.
\input{name_and_mission_statement}

\section{Membership}
\begin{enumerate}
	\item The provisions of this section must conform to the membership provisions specified in ACM's Bylaws (Bylaw 5, Section 5; ACM Constitution Article 3).
	\item Membership in the Student Chapter shall be open to all ACM members and nonmembers.
	\item Voting membership in the Student Chapter shall be granted to all active ACM UMN chapter members.
	\item Membership shall not be restricted according to nationality, race, creed, age, sex, gender identity, sexual orientation, disability, economic status, veteran status, or familial status.
\end{enumerate}

\section{Officers}
\begin{enumerate}
	\item The required Officers of this Chapter shall be: Chair, Vice Chair, and Treasurer. These Officers form the Executive Committee. These individuals must be ACM Student Members. In addition, a Faculty Sponsor with an ACM Professional Membership is required to be an officer. A minimum of three officers are needed to establish a Chapter. Other officers may also be established by a majority vote of a quorum.
	\item All required Officers of the Chapter must be members of ACM.
	\item Officers shall be elected by a plurality of the votes cast at the annual election meeting. Elected Officers serve one year terms. It is recommended that the election meeting be the last meeting in the spring, followed by a transition dinner with the previous and newly elected officers.
	\item Appointment or nomination of an individual to an officer position within an ACM chapter shall be in general limited to two full consecutive terms in the same position.  This recommendation is intended to promote the continuing infusion of new volunteers into the organization and to encourage office holders to give thought to planning for their successor.  Appointment or nomination to a third or subsequent consecutive term should be limited to situations where there is a lack of suitable nominees.
\end{enumerate}

\section{Officer Duties}
\begin{enumerate}
	\item The Chair is the principal officer and is responsible for leading the Chapter and managing its activities in accordance with the policies and procedures of the ACM and these bylaws. The Chair shall preside at all meetings of the chapter.
	\item The Vice Chair shall preside at meetings in the absence of the Chair, assist the Chair in the management of the Chapter, and perform other duties that may be assigned by the Chair.
	\item The Treasurer shall keep the minutes of all Chapter and Executive Council meetings and maintain the chapter's financial records. Other duties include:
		\begin{enumerate}
			\item Collecting dues, pay all bills, and maintain records for the chapter
			\item Preparation of the Chapter's annual report and officer contact information, and submission of these to ACM Headquarters via the Chapter Administrative Interface.
			\item Submission of any proposed amendment to these bylaws to the ACM Chief Operating Officer. Proposed amendments must be approved before they can be submitted to the Chapter's membership for a vote.
			\item Perform other duties as assigned by the Chair.
		\end{enumerate}
	\item  The Faculty Sponsor shall be a faculty member or full-time staff member of the University of Minnesota Twin Cities. Each Student Chapter has one Sponsor.
		\begin{enumerate}
			\item The Faculty Sponsor shall be a voting member of ACM and either a member of the faculty or full-time staff of the University of Minnesota Twin Cities.
			\item The Faculty Sponsor shall be generally responsible for the activities of the Chapter. Specifically, the Sponsor:
			\item Provides continuity from year to year, remaining a constant presence as student leadership and personnel change.
			\item Promotes good student-faculty relationships.
			\item Ensures that the policies and standards of the University are upheld in all activities of the Chapter.
			\item Exercises financial supervision, if necessary, by promoting prompt payment of bills and collection of dues as well as overseeing the settlement of all accounts in the event of dissolution of the Chapter.
			\item Represents the Chapter’s interests to faculty and administrators.
		\end{enumerate}
\end{enumerate}

\section{Meetings}
\begin{enumerate}
	\item The Chapter shall hold meetings only in places that are open and accessible to all members of the Association.
	\item The Annual Election meeting should be held at one of the last meetings of the academic year. At this meeting, the Treasurer will present the required reports. Also, the election of officers shall be held.
	\item Notices of meetings shall be distributed to all members at least one week prior.
\end{enumerate}

\section{Disbursements and Dues}
\begin{enumerate}
	\item Disbursements from the Treasury for Chapter expenditures shall be made by one of the Required Officers and shall be included in meeting minutes.
	\item Dues shall be fixed annually.
\end{enumerate}

\section{Amendment and Voting Procedure}
\begin{enumerate}
	\item All proposed changes to these Chapter Bylaws shall be approved by the ACM Chair before being presented to the Chapter membership for a vote.
	\item No official business of the Chapter shall be conducted unless a quorum is present. A quorum of the Officers shall be defined as a majority of the Officers or two Officers and one quarter of Members.
	\item A majority of votes of members composing quorum shall be required to carry a motion.
\end{enumerate}

\section{Code of Conduct}
\begin{enumerate}
	\item Harassment is defined as unwelcome or hostile behavior, including speech that intimidates, creates discomfort, or interferes with a person's participation or opportunity for participation in a conference, event or program. Harassment in any form, including but not limited to harassment based on alienage or citizenship, age, color, creed, disability, marital status, military status, national origin, pregnancy, childbirth- and pregnancy-related medical conditions, race, religion, sex, gender, veteran status, sexual orientation or any other status protected by laws in which the conference or program is being held, will not be tolerated. Harassment includes the use of abusive or degrading language, intimidation, stalking, harassing photography or recording, inappropriate physical contact, sexual imagery and unwelcome sexual attention. A response that the participant was ``just joking,'' or ``teasing,'' or being ``playful,'' will not be accepted.
	\item Anyone witnessing or subject to unacceptable behavior should notify a chapter officer or ACM Headquarters.
	\item All members of ACM UMN and participants in the chapter’s events are expected to abide by the University of Minnesota’s Student Conduct Code.
	\item Individuals violating these standards may be sanctioned or excluded from further participation at the discretion of the chapter officers or responsible committee members.
\end{enumerate}

\section{Dissolution of the Chapter}
\begin{enumerate}
	\item Dissolution of this Chapter by consent of the members shall consist of unanimous agreement of all its officers together with a majority vote at a meeting. This meeting must have been publicized at least two weeks in in advance to all members of the Chapter as for the purpose of taking this vote of dissolution.
	\item Should the Chapter be dissolved, its assets and liabilities shall be transferred to ACM and shall be supervised by the ACM Finance Director.  Funds given to the chapter from the University shall be returned to the University.
\end{enumerate}

\end{document}

