\input{formatting}

\begin{document}
\maketitlepage{Constitution}

\section{General}

% These are included from an external file so that they remain synchronized
% with the ones in the bylaws.
\input{name_and_mission_statement}

\subsection{Statement of Nonprofit Status}
\begin{enumerate}
	\item ACM UMN shall operate as a 501(c)(3) nonprofit organization as defined by the Internal Revenue Service.
\end{enumerate}

\subsection{Relationship to the University of Minnesota}
\begin{enumerate}
	\item ACM UMN is a Campus Life Program (CLP) of the University of Minnesota, Twin Cities and shall abide by the rules and policies of the University of Minnesota pertaining to campus life program.
	\item ACM UMN is associated with the Computer Science \& Engineering (CS\&E) Department. As such we receive funding from the department, they assist us with promotion and events, and we retain an EFS number for within-campus expenses.
\end{enumerate}

\subsection{Non-Discrimination Policy}
\begin{enumerate}
	\item ACM UMN shall not discriminate against any person on the basis of gender identity; sexual orientation; sex; race and ethnicity; color; age; disability; socioeconomic status or background; religious or spiritual beliefs or lack thereof; political affiliation; public assistance status; veteran status; marital or familial status; national origin; residential status; or openness of any of the aforementioned.
\end{enumerate}

\section{Membership}

\subsection{Eligibility}
\begin{enumerate}
	\item Any person or institution subscribing to the purposes of the Association and eligible for membership in accordance with this Constitution and Bylaws will become a member upon the acceptance of written or verbal application for membership and the payment of dues in accordance with the Bylaws. Persons presently serving as Officers are not required to pay dues.
\end{enumerate}

\subsection{Classes of Membership}
\begin{enumerate}
	\item Classes of membership and their qualifications and privileges are defined in the Bylaws. The terms ``Member'' and ``Member of the Association'' appearing without a qualifier shall refer only to members  that have voting rights at the Association level.
\end{enumerate}

\subsection{Resignation}
\begin{enumerate}
	\item A member may at any time file for resignation by submitting a written statement to the Secretary or the official ACM UMN email address, \email. Resignation shall become effective as of the date it is filed. Dues may not be refunded.
\end{enumerate}

\subsection{Admonition, Suspension and Expulsion}
\begin{enumerate}
	\item A member of the Association may be admonished, suspended or expelled for failure to pay dues, demonstrating lack of integrity, or violation of Rules, after agreement by the executive committee. A former member of the Association who has been expelled from membership may become a member only after approval of their application by a majority vote of a quorum.
\end{enumerate}

\section{Required Officers}

\subsection{Titles}
\begin{enumerate}
	\item The officers of the Association shall be at least a Chair, a Vice-Chair, a Treasurer, a Faculty Sponsor, and two additional officers.
	\item The Chair, Vice-Chair, and Treasurer are referred to as the Executive Committee, and must be ACM Student Members.
	\item In addition, the Faculty Sponsor is required to have an ACM Professional Membership.
\end{enumerate}

\subsection{The Chair}
\begin{enumerate}
	\item The Chair shall act as chair of the Executive Committee and of the Officers and shall appoint the chairs of all other committees, except as otherwise provided in this Constitution and Bylaws.
\end{enumerate}

\subsection{The Vice-Chair}
\begin{enumerate}
	\item In the temporary absence or incapacity of the Chair, the Vice-Chair shall act as chair of the Executive Committee and of the Officers. In the absence of both Chair and Vice Chair, the Officers shall elect a Chair \textit{pro tempore} from among its membership to act for a period to be determined by the Officers.
\end{enumerate}

\subsection{The Treasurer}
\begin{enumerate}
	\item The Treasurer, or other assigned officer, shall ensure that records are kept of all proceedings, actions and meetings of the Association, the Officers, and the Executive Committee, and that the votes and minutes thereof are recorded in a book or books to be kept for that purpose.
	\item The Treasurer, or other assigned officer, shall conduct the correspondence of the Association and shall give due notice of all meetings of members, of the Officers, and of the Executive Committee.
	\item The Treasurer, or other assigned officer, shall provide for the maintenance of a list of all members of the Association, clearly designating those entitled to vote, and such list or a copy thereof shall be made available for inspection by the members at all meetings of the Association where votes of the members are taken.
	\item The Treasurer, or other assigned officer, shall provide for custody of the original of this Constitution and of the Bylaws, and of the amendments thereto.
	\item The Treasurer, or other assigned officer, shall provide for custody of the seal of the Association, and when authorized by the Officers or the Executive Committee shall affix it to any instrument of the Association requiring a seal.
	\item The Treasurer shall ensure that dues and other sums are collected, that all properly approved bills are paid, and that financial statements and budgets are prepared. The Treasurer shall render to the Officers or the Executive Committee, as required, an accurate account of all transactions and of the financial condition of the Association. These are referred to as the required reports.
\end{enumerate}

\subsection{The Faculty Sponsor}
\begin{enumerate}
	\item The Faculty Sponsor shall be a voting member of ACM and either a member of the faculty or full-time staff of the University of Minnesota Twin Cities.
	\item The Faculty Sponsor shall be generally responsible for the activities of the Chapter. Specifically, the Sponsor:
	\item Provides continuity from year to year, remaining a constant presence as student leadership and personnel change.
	\item Promotes good student-faculty relationships.
	\item Ensures that the policies and standards of the University are upheld in all activities of the Chapter.
	\item Exercises financial supervision, if necessary, by promoting prompt payment of bills and collection of dues as well as overseeing the settlement of all accounts in the event of dissolution of the Chapter.
	\item Represents the Chapter’s interests to faculty and administrators.
\end{enumerate}

\subsection{The Additional Officers}
\begin{enumerate}
	\item The Additional Officers shall be appointed by the Executive Committee from the pool of the elected officials. 
\end{enumerate}

\subsection{Disbursements and Dues}
\begin{enumerate}
	\item Disbursements from the Treasury for Chapter expenditures shall be made by one of the Required Officers and shall be included in meeting minutes.
	\item Dues shall be fixed annually.
\end{enumerate}

\section{Executive Committee}

\subsection{Composition and Authority}
\begin{enumerate}
	\item The Executive Committee shall consist of the Chair, the Vice-Chair, the Treasurer, the Past Chair and other members of Officers as prescribed by the Bylaws.
	\item The Executive Committee shall be bound by any action taken by the Officers or the Association. The Executive Committee shall appoint representatives of the Association for specific purposes, and shall in general manage the affairs of the Association between Officer meetings except in those matters for which Officers action is required by the Constitution or Bylaws. The Chair shall call a meeting of or cause questions to be presented to the Executive Committee upon the request of any member of the Committee.
\end{enumerate}

\subsection{Authority to Act Without Meeting}
\begin{enumerate}
	\item Any resolution adopted by majority vote of the members of the Executive Committee after due notice to each of its members shall be deemed and considered the act of the Executive Committee as though adopted at an actual meeting of the Committee whether or not on the occasion of the vote there was an actual meeting of the Committee. The notice and the voting of the members of the Committee may be by mail, telephone, telegraph, electronic communication, or personally, or by any combination of these, and notice by mail or telegram shall be deemed given when sent to the Committee member's last mailing address. A record of the notice and of the voting and of the manner in which the action was taken shall be noted in the minutes of the Committee.
\end{enumerate}

\subsection{Place of Meeting}
\begin{enumerate}
	\item Meetings of the Executive Committee shall be at the principal office of the Association, or at the place of and in connection with a meeting of the Association, or at such places as the Executive Committee may determine.
\end{enumerate}

\section{Officers}

\subsection{Membership}
\begin{enumerate}
	\item All Required Officers are required to be Members of the Association.
	\item Officers of the group will be currently enrolled University of Minnesota - Twin Cities campus student who are registered for at least six credits. Graduate and Professional students can be exempted from the credit requirement with documentation from their program signifying the student is actively pursuing a degree. Officers must also be in good standing with the University and free from any sanctions as defined in the Board of Regents Policy - Student Conduct Code, administered by the Office for Community Standards. 
\end{enumerate}

\subsection{New Officer Positions}
\begin{enumerate}
	\item New officer positions may be established by a majority vote of quorum.
	\item An officer may be Titled or Untitled.
	\item Untitled Officers may be referred to as General Officers.
\end{enumerate}

\subsection{Authority and Duties}
\begin{enumerate}
	\item The Officers shall formulate the policies of ACM UMN, and generally supervise their execution. Each Officer shall represent the members and the best interests of the Association.
	\item Each officer of the Association shall be bound by any action taken by the Officers or the Association and shall have such additional authority and duties as may be conferred by the Bylaws or resolution of the Officers.
\end{enumerate}

\subsection{Meetings}
\begin{enumerate}
	\item The Officers shall meet weekly. A quorum of the Officers shall consist of a majority of the Titled Officers, or two Officers and one quarter of Members.
	\item The Chapter shall hold meetings only in places that are open and accessible to all members of the Association.
	\item An Officer unable to be present at a meeting may appoint a Member of the Association as the Officer’s proxy. The proxy may take part in discussion and may vote in the place of the Officer. While so acting as a proxy for the Officer, the proxy shall be deemed for all purposes to have the powers of that Officer for whom they stand in, but only in the absence of the replaced Officer. Proxy appointment shall not be longer than one meeting in duration.
	\item Except where by law or by this Constitution a meeting of the members of the Officers or their proxies requires their physical presence at the same time and place, the Officers may transact business by mail, electronic communications, in the physical presence of each other, or by any combination of these means. Any resolution adopted in such manner by a majority vote of a quorum of the members of the Officers (or by such larger vote as may be required by law or by this Constitution or the Bylaws), after due notice is given to its members shall be deemed and considered the act of the Officers as though adopted at a meeting of the Officers. Notice by mail or electronic communications shall be deemed given when sent to the Officers member's last address. A record of the notice and of the voting and of the manner in which the action was taken shall be noted in the meeting minutes.
	\item Actual meetings of the Officers are required to be held at least once in Spring Semester and once in Fall Semester.
\end{enumerate}

\subsection{Annual Report}
\begin{enumerate}
	\item The Officers shall report annually to the members of the Association through the medium of the ACM UMN Newsletter or another of the Association's publications which is sent to all members. An annual report shall also be submitted to ACM National in accordance with their requirements for student chapters.
\end{enumerate}

\subsection{Annual Budget}
\begin{enumerate}
	\item Each year, the Officers shall adopt an annual budget authored at least in part by the Treasurer. This budget shall guide the fiscal affairs of the Association for the following fiscal year.
\end{enumerate}

\subsection{Questions}
\begin{enumerate}
	\item The Officers shall give members of the Association reasonable opportunities to express their views on presented questions to the Association upon request of the inquisitor. Upon petition of one percent of the Members of the Association or by decision of a majority of the Officers, a question to the Association shall be submitted without undue delay to a ballot of the Association as provided in the Bylaws. The majority vote where quorum is present shall be binding upon the Officers, except where a larger vote is required by law and except in the case of an amendment to this Constitution or the Certificate of Incorporation.
\end{enumerate}

\subsection{ACM Code of Professional Ethics}
\begin{enumerate}
	\item The Officers shall adopt, maintain, enforce, and conspicuously publish and display to all members and the public a code of professional ethics, which shall be binding on all members of the Association.
\end{enumerate}

\section{Elections}
\begin{enumerate}
	\item The Chair, Vice-Chair, Treasurer and as many Officers as are required to fill Officer vacancies shall be elected as of the end of Spring Semester every year by the Members of the Association. The constituency eligible to vote for other Officers shall be defined in the bylaws. Balloting shall be conducted and recorded as provided in the bylaws.
	\item No person may hold two Officer positions simultaneously.
	\item Appointment or nomination of an individual to an officer position within ACM UMN shall be limited to two full consecutive terms in the same position.
\end{enumerate}

\begin{enumerate}
	\item Officers shall be elected by a plurality of the votes cast at the annual election meeting.
\end{enumerate}

\section{Tenure}

\subsection{Officers}
\begin{enumerate}
	\item All officers shall be elected for one year terms.
	\item If any vacancy arises in an Officer position, the Executive Committee shall fill it by appointment until the next regular election, unless otherwise proscribed by the Bylaws.
\end{enumerate}

\subsection{Recall}
\begin{enumerate}
	\item Any elected Officer may be recalled by vote of the Members following an impeachment. Impeachment must be by a vote of one fourth of members present where quorum exists. Upon impeachment, the Officers shall promptly direct a special ballot by all Members. A majority vote of the votes given quorum will suffice for immediate removal of an Officer from their Officer position.
\end{enumerate}

\section{Nominations}
\begin{enumerate}
	\item Members shall be notified of nominations for Officers as provided in the Bylaws. Prior to distribution of the ballot, nominations by petition of at least one percent of the Members of the constituency shall be received and entered on the ballot in the manner described in the Bylaws.
\end{enumerate}

\section{Association Meetings by Ballot}
\begin{enumerate}
	\item With respect to any question or vote required by law to be submitted to or taken by the Members of the Association at a meeting of the Members, the timely emailing of the ballot or other notice to each Member at the last email address as given to the Treasurer, or other appointed officer, shall be deemed and considered notice of a meeting of the Association; the return of the ballot shall be deemed a counted vote. Each Member of the Association, however, shall have the privilege of attending in person at the time and place stated in the ballot or other notice for the opening and counting of the ballots, and the Member may cast a vote personally instead of by online ballot.
\end{enumerate}

\section{Bylaws}
\begin{enumerate}
	\item Bylaws may be adopted or amended by a majority vote of quorum. The Officers shall have the authority to interpret the Bylaws.
\end{enumerate}

\section{Amendments}

\subsection{Constitution}
\begin{enumerate}
	\item This Constitution may be amended by an affirmative majority vote of quorum. Proposed amendments to this Constitution shall be submitted to the quorum for ballot upon an affirmative vote of two-thirds where quorum exists.
\end{enumerate}

\subsection{Notification}
\begin{enumerate}
	\item Any additions or changes in the Constitution or the Bylaws shall be reported by the Treasurer, or other appointed officer, to the membership by mail, e-mail, or publication in one of the Association's publications received by all members.
\end{enumerate}

\section{Dissolution of the Chapter}
\begin{enumerate}
	\item Dissolution of this Chapter by consent of the members shall consist of unanimous agreement of all its officers together with a majority vote at a meeting. This meeting must have been publicized at least two weeks in in advance to all members of the Chapter as for the purpose of taking this vote of dissolution.
	\item Should the Chapter be dissolved, its assets and liabilities shall be transferred to the University of Minnesota.

\end{enumerate}

\signatures{5}

\end{document}
